---
title: "FLO replications - GLMMs"
author: "Eva"
date: "6/15/2020"
output: html_document
---
```{r}
rm(list = ls())
```

Set your local working directory. This should be (and is assumed to be in the rest of the code) the highest point in your local folder:
```{r}
localGitDir <- 'C:/Users/eva_v/Documents/GitHub/leverhulmeNDL'
```

```{r}
library(lmerTest)
```


# load preprocessed files

```{r}
pictureLabel <-read.table(paste(localGitDir, "/exp1/data/pictureLabel.txt", sep = ""), header = T, stringsAsFactors = T)

labelPicture <-read.table(paste(localGitDir, "/exp1/data/labelPicture.txt", sep = ""), header = T, stringsAsFactors = T)

humansTypeWeigths <-read.table(paste(localGitDir, "/exp1/data/humansTypeWeigths.txt", sep = ""), header = T, stringsAsFactors = T) #this is the contingency judgement task with the type of match/mismatch trials

```

Subjects that scored <=.7 and/or had >3 timeouts in the random dot task (attention check)
```{r}
badsubjs<-c("1414932", "1422463", "1431981", "1458997", "1459696", "1422470", "1422475", "1422689", "1431942", "1431944", "1431956", "1432003", "1459001", "1459009", "1459036", "1459057", "1459078", "1459703", "1420171", "1422680", "1432009", "1420199", "1431960", "1431997", "1459020")
```

# Load functions from the lab repo

```{r}
urlFolder <- 'https://api.github.com/repos/n400peanuts/languagelearninglab/git/trees/master?recursive=1'
urlRaw <- 'https://raw.githubusercontent.com/n400peanuts/languagelearninglab/master/tools/'

loadFunctionsGithub <-function(urlFolder, urlRaw){
  if (!require(httr)) {
    stop("httr not installed")
  } 
  else if (!require(RCurl)){
    stop("RCurl not installed") 
  }
  else {
    print('----loading. Please wait----')
  };
  httr::GET(urlFolder)-> req
  stop_for_status(req)
  filelist <- unlist(lapply(content(req)$tree, "[", "path"), use.names = F)
  urlFunctions <- grep("docs/tools/", filelist, value = TRUE, fixed = TRUE)
  gsub("docs/tools/", "", urlFunctions) -> functions
  for (i in 1:length(functions)){
    RCurl::getURL(paste0(urlRaw, functions[i]), ssl.verifypeer = FALSE)-> temp
    eval(parse(text = temp), envir = .GlobalEnv)
  };
}

loadFunctionsGithub(urlFolder = urlFolder, urlRaw = urlRaw);
rm(urlFolder, urlRaw, loadFunctionsGithub)
```
# GLMMs - picture label
```{r}
pictureLabel$frequency <- as.factor(pictureLabel$frequency)

pictureLabel$learning = relevel(pictureLabel$learning, ref = "LF")
pictureLabel$frequency = relevel(pictureLabel$frequency, ref = "low")
pictureLabel <- lizCenter(pictureLabel, list("learning" , "frequency", "task"))

```

```{r}
piclab_model <- glmer(acc ~  frequency.ct*learning.ct + (frequency.ct|subjID), 
         data = pictureLabel[pictureLabel$rt > 100 & !(pictureLabel$subjID %in% badsubjs),], 
         family="binomial",
         control=glmerControl(optimizer = "bobyqa"))

adjusted.piclab_model = adjust_intercept_model(piclab_model, chance = log(0.33/(1-0.33)))
round(adjusted.piclab_model,5)

```

# GLMMs - Label picture

```{r}
labelPicture$frequency <- as.factor(labelPicture$frequency)
plyr::revalue(labelPicture$frequency, c("25"="low"))-> labelPicture$frequency;
plyr::revalue(labelPicture$frequency, c("75"="high"))-> labelPicture$frequency;

labelPicture$learning = relevel(labelPicture$learning, ref = "LF")
labelPicture$frequency = relevel(labelPicture$frequency, ref = "low")
labelPicture <- lizCenter(labelPicture, list("learning" , "frequency"))

```

```{r}
labpic_model <- glmer(acc ~  frequency.ct*learning.ct + (frequency.ct|subjID), 
         data = labelPicture[labelPicture$rt > 100 & labelPicture$rt <=2500 & !(labelPicture$subjID %in% badsubjs),], 
         family="binomial",
         control=glmerControl(optimizer = "bobyqa"))

adjusted.labpic_model = adjust_intercept_model(labpic_model, chance = log(0.33/(1-0.33)))
round(adjusted.labpic_model,5)

```

# LMMs Contingency Judgement task:
```{r}
humansTypeWeigths$learning = relevel(humansTypeWeigths$learning, ref = "FL")
humansTypeWeigths$frequency = relevel(humansTypeWeigths$frequency, ref = "low")

```


```{r}
#Match
humansTypeWeigths<-lizCenter(humansTypeWeigths, list("frequency", "learning"))

lm1<-lmer(resp ~ frequency.ct * learning.ct  +(frequency.ct|subjID), data = humansTypeWeigths[humansTypeWeigths$type=="match",])

round(summary(lm1)$coefficients,5)
```
```{r}
#Mismatch-type1

lm2<-lmer(resp ~ frequency.ct * learning.ct  +(frequency.ct|subjID), data = humansTypeWeigths[humansTypeWeigths$type=="mismatch-type1",])

round(summary(lm2)$coefficients,5)
```

# Combine both generalization tasks in one dataset

I'm going to combine both generalization tasks in one single dataset called genTask because this is the dataset that needs to be compared with Mike's data.

Reload the data:

```{r}
pictureLabel <-read.table(paste(localGitDir, "/exp1/data/pictureLabel.txt", sep = ""), header = T, stringsAsFactors = T)
labelPicture <-read.table(paste(localGitDir, "/exp1/data/labelPicture.txt", sep = ""), header = T, stringsAsFactors = T)
```

```{r}
genTask <- rbind(labelPicture[labelPicture$rt > 100 & !(labelPicture$subjID %in% badsubjs),], 
                 pictureLabel[pictureLabel$rt > 100 & !(pictureLabel$subjID %in% badsubjs),])

genTask$frequency <- as.factor(genTask$frequency)
plyr::revalue(genTask$frequency, c("25"="low"))-> genTask$frequency;
plyr::revalue(genTask$frequency, c("75"="high"))-> genTask$frequency;
```

```{r}
genTask$learning = relevel(genTask$learning, ref = "LF")
genTask$frequency = relevel(genTask$frequency, ref = "low")
genTask <- lizCenter(genTask, list("learning" , "frequency", "task"))
```

```{r model generalization tasks together}
genTask_model <- glmer(acc ~  frequency.ct*learning.ct + task.ct + (frequency.ct|subjID) , 
         data = genTask, 
         family="binomial",
         control=glmerControl(optimizer = "bobyqa"))

adjusted.genTask_model = adjust_intercept_model(genTask_model, chance = log(0.33/(1-0.33)))
round(summary(genTask_model)$coefficients,5)
```

# BF based on the fmri data

```{r}
fmri<-read.table(paste(localGitDir, "/prereg/fmri.txt", sep = ""), header = T)
```

From Mike's excel about bad subjects:
```{r}
fmriClean<-fmri[!(fmri$subjID==1  & fmri$learning=="sx") &
                  !(fmri$subjID==14 & fmri$learning=="sx") &
                  !(fmri$subjID==22 & fmri$learning=="sx") &
                  !(fmri$subjID==3 & fmri$learning=="sx") &
                  !(fmri$subjID==4 & fmri$learning=="xs") &
                  !(fmri$subjID==7 & fmri$learning=="xs") &
                  !(fmri$subjID==10 & fmri$learning=="xs")&
                  !(fmri$subjID==12 & fmri$learning=="xs"),]

```

```{r}
#let's center the variables. 
fmriClean$frequency <- as.factor(fmriClean$frequency)
fmriClean$learning<-as.factor(fmriClean$learning)
fmriClean$testing<-as.factor(fmriClean$testing)
fmriClean$trialType<-as.factor(fmriClean$trialType)

#relevel
fmriClean$learning <- relevel(fmriClean$learning, ref = "sx")
fmriClean$frequency <- relevel(fmriClean$frequency, ref = "l")
fmriClean<-lizCenter(fmriClean, listfname = list("learning" , "frequency"))
```

```{r}
fmriglmer1<-glmer(acc ~  frequency.ct*learning.ct + (frequency.ct|subjID), 
      data = fmriClean[!(fmriClean$trialType=="control"),], # "control" are blue fribbles, so we need to remove it.
      family="binomial",
      control=glmerControl(optimizer = "bobyqa"))
round(summary(fmriglmer1)$coefficients,4)
```
## Frequency

```{r}
#main effect of frequency from Mike's data:
round(summary(fmriglmer1)$coefficients[2,],4)
```

```{r}
#main effect of frequency from our pilot data:
round(summary(genTask_model)$coefficients[2,],4)
```
```{r}
Bf(sd = .2612, 
   obtained = 1.6818, 
   uniform = 0, 
   sdtheory = 0.2483, 
   meanoftheory = 1.7025, 
   tail = 1)
```
## learning

```{r}
#main effect of learning from Mike's data:
round(summary(fmriglmer1)$coefficients[3,],4)
```

```{r}
#main effect of learning from our pilot data:
round(summary(genTask_model)$coefficients[3,],4)
```
```{r}
Bf(sd = 0.2708, 
   obtained = 0.4785, 
   uniform = 0, 
   sdtheory = 0.1427, 
   meanoftheory = 0.5893, 
   tail = 1)
```
## frequency by learning interaction

```{r}
#interaction between frequency and learning from Mike's data:
round(summary(fmriglmer1)$coefficients[4,],4)

```

```{r}
#interaction between frequency and learning from our pilot data:
round(summary(genTask_model)$coefficients[5,],4)

```
```{r}
Bf(sd = 0.5204, 
   obtained = 0.2826, 
   uniform = 0, 
   sdtheory = 0.2615, 
   meanoftheory = 1.0265, 
   tail = 1)
```
